\bf Probabilistic Forecasts in Hierarchical~Time~Series

### 2020-01-25 R1/Response.tex

	    \textit{The best performing reconciliation method is MinT with shrinkage, but the authors never state	the value of the shrinkage parameter or how it was chosen.  Similarly, they compare with variance scaling without explaining what they mean by variance scaling.}\\

	    The shrinkage estimator is that of Sch\"afer and Strimmer~(2005). Details on this method (including the choice of shrinkage parameter) are now provided.  Similarly, we now provide more detail on variance scaling, which simply refers to using the variance of one step ahead in-sample forecast errors.\\

	    \textit{In addition to the above mentioned shortcomings, I think the authors should reconsider their empirical evaluation. Maybe a second case study or a simulation study is needed to show the value of the geometric insights provided. We already know that MinT is better than OLS and WLS. What is the new and better reconciliation approach that has come from the geometric insights?}\\

		The objective of this paper is not to propose a new and better reconciliation approach but to establish new results that lead to clearer understanding of the properties of existing methods.  Therefore, while the paper does not include a new method, it does provide insights into how new methods should (or should not) be developed.  For examples of this, see the discussion on page 19 just before Section 4.1 and comments in the conclusion.\\

		In this paper, the purpose of the empirical evaluation is to provide a demonstration of the theoretical results that we have established.  We agree that this could be improved.  We have greatly expanded Section 5.2 to more clearly investigate two different loss functions and demonstrate two different understandings of optimality.\\

		Improving the existing empirical application in the ways suggested by the referee has lengthened the paper considerably.  Therefore, we prefer to refrain from including a second empirical demonstration.\\

@@

		\item \textit{Improvement guarantees: The boxplot in Figure 8 shows that OLS always improves MSE, while this is not the case for the other reconciliation approaches. To gain a better understanding of the implications of Theorem 3.2, it would be useful to show that the other approaches always
		improve accuracy in their transformed spaces.}\\

	    We now expand section 5.2 to report results for two different error metrics.  Furthermore we have added additional insights in Section 3.4 that are now also demonstrated in this section.  In particular we show that while the distance reducing property of Theorem 3.2 depends entirely on the choice of loss function, minimising the expected loss function can always be achieved by a MinT approach. TO DO.\\

@@

		\textit{What is the interpretation of the transformed spaces and can the authors make the connection	between these spaces and the choice of reconciliation approach and error measure more clear?}\\

	    Reflecting on this issue has led us towards making a number of changes.  To reiterate, we may define a loss function based on the notion of Euclidean distance.  In this case an orthogonal projection is guaranteed to lead to reconciled forecasts that are better than base forecasts.  Alternatively we may define a more general loss function, for instance by taking weights into account.  In this case, it is an orthogonal projection in the \textit{transformed} space that has the same optimality properties.\\

	    Now consider the property of minimising expected loss when the loss is function based on Euclidean distance.  This can be achieved by the MinT estimator.  We now provide a new result proving that minimising the expected loss in a transformed space in fact leads to the same MinT estimator.\\

	    To make the transformed space more interpretable we consider a new loss function that is driven by the example used in our empirical evaluation.  This is a loss function weighted by ... TO DO

### 2020-01-25 R1/Letter.tex
changes made to response and letter in light of the fact that GMinT doesnt work

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We introduce a modification of MinT that should be implemented in contexts where some user defined loss function is sensible.  Using the empirical example, we demonstrate that this generalised version of MinT takes both the nature of the loss function and dependence between forecast errors into account and outperforms a standard implementation of MinT and WLS.
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  Where differences in forecast accuracy are significant.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
\end{enumerate}

>>>>

Please find attached a revised manuscript for ``Forecast reconciliation: a geometric view with new insights on bias correction" by Anastasios Panagiotelis, Puwasala Gamakumara, George Athanasopoulos and Rob Hyndman for your consideration for publication in International Journal of Forecasting. We are very excited to have been given the opportunity to revise and resubmit. We carefully considered the comments offered by the two reviewers. Herein, we briefly summarize the major changes in the revision:
\begin{enumerate}
	\item We have greatly expanded the empirical study including more measures of forecast accuracy (including those specifically measuring bias).  This has led to the insight that reconciliation alone can in fact reduce the bias of an estimator.  Where differences in forecast accuracy are significant.
	\item We introduce some new results about MinT that make it clear that MinT minimises expected loss for a wider range of loss functions than previously thought.
	\item We now reflect on some issues that were not discussed in the previous version of the manuscript including the role of non-negativity, 
\end{enumerate}
